Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
nothing, adds space

#Visualizing rules
```{r}
#look at counts
ggplot(for_plots, aes(LHS))+
  geom_bar()

@@

##TO MOVE UP (These are ready:)
Rounds grades and add new row from original grade up to 10.
NOTE: includes mandatory courses.
```{r}
distributed_transcript <- d_transcript %>%
  filter(!is.na(Grade), Grade>=0) %>%
  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
         Values = T) %>%
  spread(key = "Round_grade", value = Values) %>%
  mutate(g1  = g0|g1,
         g2  = g1|g2,
         g3  = g2|g3,
         g4  = g3|g4,
         g5  = g4|g5,
         g6  = g5|g6,
         g7  = g6|g7,
         g8  = g7|g8,
         g9  = g8|g9,
         g10 = g9|g10
         ) %>%
  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
  select(-Gr_bool )%>%
  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
  select(-Trash) %>%
  mutate(Grade= as.numeric(Grade_new))%>%
  select(-Grade_new) #%>%
  #to check that the grades appear from original grade to 10.
  #arrange(`Student ID`, `Course ID`) 
```

>>>>

```
#Experiments
#Visualizing rules
```{r}
#look at counts
ggplot(for_plots, aes(LHS))+
  geom_bar()

@@

##TO MOVE UP (These are ready:)
Rounds grades and add new row from original grade up to 10.
NOTE: includes mandatory courses.
```{r}

distributed_transcript <- d_transcript %>%
  filter(!is.na(Grade), Grade>=0) %>%
  mutate(Round_grade = paste("g", round(Grade,0),sep=""),
         Values = T) %>%
  spread(key = "Round_grade", value = Values) %>%
  mutate(g1  = g0|g1,
         g2  = g1|g2,
         g3  = g2|g3,
         g4  = g3|g4,
         g5  = g4|g5,
         g6  = g5|g6,
         g7  = g6|g7,
         g8  = g7|g8,
         g9  = g8|g9,
         g10 = g9|g10
         ) %>%
  gather(key="Gr_string", value="Gr_bool", g0, g1, g2, g3, g4,g5,g6,g7,g8,g9,g10, na.rm=T) %>%
  select(-Gr_bool )%>%
  separate(Gr_string, into=c("Trash", "Grade_new"), sep="g")%>%
  select(-Trash) %>%
  mutate(Grade= as.numeric(Grade_new))%>%
  select(-Grade_new) #%>%
  #to check that the grades appear from original grade to 10.
  #arrange(`Student ID`, `Course ID`)
